\input{preface}

\begin{document}

\title{Young massive stars fed along filaments in W51}
\titlerunning{W51 EVLA H2CO}
\authorrunning{Ginsburg et al}
\input{authors}

\date{Date: \today ~~ Time: \currenttime}

\abstract
{This is an abstract.}
{To fill it in.}
{Please write your own version of this and send it to Adam.
Also, title suggestions are welcome!}
{We have filled it in.}
{The abstract is done.}

\maketitle

\todo{To-do items are coded in red.}

\section{Introduction}
\section{Observations}
\section{Analysis}
\subsection{\formaldehyde emission features}
While \formaldehyde \oneone and \twotwo are commonly observed in absorption,
the \oneone line has only been observed in emission in our galaxy as a maser
\citep{}.  The \twotwo line has been observed in emission only  in the
starburst M82, and there very weakly \citep{Mangum2008a}.

We have detected 3 regions of \twotwo emission in the W51 region.  The bright
maser source W51e2 is partially surrounded by a `halo' of \formaldehyde \twotwo
emission to its northeast; the \hchii region itself shows only \twotwo
absorption because the continuum source has a high brightness temperature.  The
\hchii region W51e8 exhibits extended \twotwo emission, including a somewhat
diffuse region stretching between W51e4 and W51e1.  Finally, in W51 IRS 2,
there is extended \twotwo emission stretching between W51d1 and W51d2, adjacent
to the ammonia masers observed by \citet{Zhang1995a} and more recently
\citet{Goddi2015a}, and very close to (but not perfectly correlated with) the
\citet{Zapata2010a} W51 North Disk.

In all cases, the emission is extended and spread over multiple velocity
channels.  It is therefore not maser emission.

None of these detections have corresponding \oneone emission.  There are two possible
explanations for these nondetections, given our sensitivity: 


\section{Conclusion}

\textbf{Acknowledgements}:

\textbf{Code Packages Used}:

\begin{itemize}
    \item aplpy \url{http://aplpy.github.io}
    \item pyradex \url{https://github.com/adamginsburg/pyradex}
    \item myRadex \url{https://github.com/fjdu/myRadex}
    \item pyspeckit \url{http://pyspeckit.bitbucket.org}
    \item aplpy \url{https://aplpy.github.io/}
    \item wcsaxes \url{http://wcsaxes.readthedocs.org}
    \item spectral cube \url{http://spectral-cube.readthedocs.org}
    \item pvextractor \url{http://pvextractor.readthedocs.org/}
\end{itemize}


\input{solobib}
\end{document}
